A demonstration of the \LaTeXe\ class file for \itshape{SAGE Publications}

### 2015-12-23 body/rbprm.tex
geometrical feasibility

We say that a root placement $\mathbf{q}^{0}$ is geometrically feasible if there exists at least one bijective mapping $\pi$
such that
\begin{equation}
    \pi\colon \quad \mathbf{q}^{0} \in  SE(3) \longrightarrow  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} 
    \label{eq:pi}
\end{equation}

The set of all geometrically feasible root placements is denoted by $C_{reach}$. By extension, a path $\mathbf{q}^0(t)$ is truly feasible if $\forall t \in [0,1], \mathbf{q}^0(t) \in C_{reach}$.

For a two-stage acyclic contact planner to be exact and complete, we need the combination of two conditions on a guide trajectory generator: all the generated trajectories must be \textit{geometrically feasible} (sufficient condition); the guide planner must be complete, i.e. it must be able to discover any truly feasible trajectory (necessary condition).

@@

\subsection{Conditions for geometric feasibility}
By default, the geometric feasibility implies a constructive demonstration by exhibiting a valid $\pi$. This is the approach chosen by \cite{Bouyarmane2009}. However, computing a valid  $\mathbf{q}^{\overline{0}}$ is costly in practice. In this section we rather define a necessary condition and a sufficient condition for geometric feasibility that do not require this explicit computation.

@@

\subsubsection*{Geometric feasibility: necessary condition}
For a contact to be possible, a volume $O_i \in O$ necessarily intersects with the reachable workspace $W(\mathbf{q}^{0})$ (Figure~\ref{fig:contact_gen}--1). Furthermore, if $\mathbf{q}^{0}$ is  feasible, then the trunk of the robot $W^0(\mathbf{q}^{0})$ is necessarily not colliding  with the environment $O$.

@@

\subsubsection*{Geometric feasibility: sufficient condition}
%~ In building $C_{reach}^1$, we directly considered the including hull of the root body $W^{0}$, obtaining a necessary condition. 
A trivial sufficient condition for geometric feasibility can be constructed as a variation of $C_{reach}^1$, by replacing $W^0$ with a bounding volume $B^{max}$ encompassing the whole robot in a given pose, except for the effector surfaces to be in contact. We denote by \mbox{$C_{reach}^\infty \subset C_{reach}$} the set of root placements corresponding to the sufficient condition.

@@

\subsection{Reachability: a compromise condition}
The sufficient condition is not interesting in practice since it leads the solver to lose too many interesting trajectories. The necessary condition is not perfect either, since the first stage of the planner would stop on a guide that is not truly feasible in practice. It might be possible to find a shape $B$ that is necessary and sufficient; however, it seems intuitively very unlikely in general. The construction of a shape $W^0 \subset B \subset B^{max}$ leading to a necessary and sufficient condition (or the proof of its nonexistence) is out of the scope of this work.

>>>>

We say that a root placement $\mathbf{q}^{0}$ is \textit{geometrically feasible} if there exists at least one bijective mapping $\pi$
such that
\begin{equation}
    \pi\colon \quad \mathbf{q}^{0} \in  SE(3) \longrightarrow  \mathbf{q}^{0} \oplus \mathbf{q}^{\overline{0}} \in C_{contact} 
    \label{eq:pi}
\end{equation}

The set of all \textit{geometrically feasible} root placements is denoted by $C_{reach}$. By extension, a path $\mathbf{q}^0(t)$ is \textit{geometrically feasible} if $\forall t \in [0,1], \mathbf{q}^0(t) \in C_{reach}$.

For this stage, and for this stage only, we make the assumption that in cluttered environments, a \textit{geometrically feasible} path can be transformed into a \textit{truly feasible} path.
Under this assumption, for a two-stage acyclic contact planner to be exact and complete, we need the combination of two conditions on a guide trajectory generator: all the generated trajectories must be \textit{geometrically feasible} (sufficient condition); the guide planner must be complete, i.e. it must be able to discover any \textit{geometrically feasible} trajectory (necessary condition).

@@

\subsection{Conditions for geometrical feasibility}
By default, \textit{geometrical feasibility} implies a constructive demonstration by exhibiting a valid $\pi$. This is the approach chosen by \cite{Bouyarmane2009}. However, computing a valid  $\mathbf{q}^{\overline{0}}$ is costly in practice. In this section we rather define a necessary condition and a sufficient condition for \textit{geometrical feasibility} that do not require this explicit computation.

@@

\subsubsection*{Geometrical feasibility: necessary condition}
For a contact to be possible, a volume $O_i \in O$ necessarily intersects with the reachable workspace $W(\mathbf{q}^{0})$ (Figure~\ref{fig:contact_gen}--1). Furthermore, if $\mathbf{q}^{0}$ is  feasible, then the trunk of the robot $W^0(\mathbf{q}^{0})$ is necessarily not colliding  with the environment $O$.

@@

\subsubsection*{Geometrical feasibility: sufficient condition}
%~ In building $C_{reach}^1$, we directly considered the including hull of the root body $W^{0}$, obtaining a necessary condition. 
A trivial sufficient condition for \textit{geometrical feasibility} can be constructed as a variation of $C_{reach}^1$, by replacing $W^0$ with a bounding volume $B^{max}$ encompassing the whole robot in a given pose, except for the effector surfaces to be in contact. We denote by \mbox{$C_{reach}^\infty \subset C_{reach}$} the set of root placements corresponding to the sufficient condition.

@@

\subsection{Geometrical feasibility: a compromise reachability condition}
The sufficient condition is not interesting in practice since it leads the solver to lose too many interesting trajectories. The necessary condition is not perfect either, since the first stage of the planner would stop on a guide that is not \textit{geometrical feasible} in practice. It might be possible to find a shape $B$ that is necessary and sufficient; however, it seems intuitively very unlikely in general. The construction of a shape $W^0 \subset B \subset B^{max}$ leading to a necessary and sufficient condition (or the proof of its nonexistence) is out of the scope of this work.

### 2015-12-23 body/results.tex
geometrical feasibility

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ TODO~\cite{Semini}.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario. Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dexterous manipulation.

>>>>

% !TEX root =  ../main.tex
\section{Results}
\label{sec:results}
In this Section we present some of the results obtained with our planner. The complete sequences computed are shown in the companion video, TODO.
Specifically, we demonstrate the planner for two really different robots, in a large variety of environments: the humanoid HRP-2 and the quadruped HyQ.
For each scenario we indicate the chosen heuristics. We also provide a performance analysis, which shows that the planner is compatible with interactive applications,
and present the success rates obtained in each scenario. Moreover, we demonstrate the interest of our robustness criterion in the different computed poses.
Finally, a last example suggests possible applications to dexterous manipulation.
